The paper on blockchain front-running

### 2018-09-28 frontrunning/Latex/main.tex
[frontrunning] more fixes, separate appendix from main
ack

\input{setup/packages}
\input{setup/macros}
\input{setup/table}

@@

\title{\Large \bf Frontrunning}
%\author{}

%\author{}
\institute{Concordia University}

@@

@@

\clearpage
\appendix

>>>>

\input{setup/packages}
\input{setup/macros}

\usepackage{draftwatermark}
\SetWatermarkAngle{90}
\SetWatermarkHorCenter{0.2\textwidth}
\SetWatermarkColor{blue}
\SetWatermarkText{Working Draft}

@@

\title{The paper on blockchain front-running}
\author{Shayan Eskandari, Seyedehmahsa Moosavi, \and Jeremy Clark}

\institute{
	Gina Cody School of Engineering and Computer Science\\ Concordia University
	}

@@

% = = = = = Ack = = = = = %

\subsubsection*{Acknowledgements.}
The authors thank the Autorit\'e des March\'es Financiers (AMF) for sponsoring this research through the Education and Good Governance Fund (EGGF), as well as NSERC through a Discovery Grant.

@@

\input{sections/appendix}
